---
title: "Prediction Types and Data Filters"
author: "Gabriel de Souza Seibel"
date: "3/7/20"
output:
html_document:
df_print: paged
html_notebook: default
pdf_document: default
---

```{r setup}
knitr::opts_knit$set(root.dir = '../..') # this should be knitted from the repo root directory
```

# Prediction Types

We'll analyse some facets of the data from ELSA. Some data filters will be implemented in order to predict:

1. **Presence** of symptoms
2. **Incidence** of symptoms
3. **Persistence** of symptoms
4. **Remission** of symptoms

Note that the presence and incidence prediction models have two variants each. The first variant includes all instances
of the respective scope ("general population"), while the second variant includes only instances that present some specific
psychological predictors (i.e. `mentalvar_A_TMC`) that motivate an assessment of the suicide ideation risk.

# Predictions Specifications

Below follows a table that summarizes some characteristics of the prediction types:

|    Model    | Predictor Wave | Predictor CIS\-R Labels Subset | Outcome Wave | Outcome CIS\-R Labels |
|-------------|----------------|--------------------------------|--------------|-----------------------|
| Presence    | 1              | \-                             | 1            | Positive              |
| Incidence   | 1              | Negative                       | 2            | Positive              |
| Persistence | 1              | Positive                       | 2            | Positive              |
| Remission   | 1              | Positive                       | 2            | Negative              |

```{r}

source("scripts/setup.R")
source("scripts/funcs/data.R")

library(future)
library(furrr)
plan(multicore)
```


```{r}
configs <- get_all_data_configs()
configs$data <- future_pmap(list(configs$mode, configs$label, configs$symptoms), get_data)
with_data <- configs

to_total_count <- function(data) { nrow(data) }
to_positive_class_count <- function(data) { data %>% filter(Class == "POSITIVE") %>% count() }
to_negative_class_count <- function(data) { to_total_count(data) - to_positive_class_count(data) }
to_positive_class_percentage <- function(data) { 100 * to_positive_class_count(data) / to_total_count(data) }
to_negative_class_percentage <- function(data) { 100 * to_negative_class_count(data) / to_total_count(data) }

configs$total <- configs$data %>% map(to_total_count) %>% unlist()
configs$positive <- configs$data %>%
  map(to_positive_class_count) %>%
  unlist()
configs$negative <- configs$data %>%
  map(to_negative_class_count) %>%
  unlist()
configs$positive_pctg <- configs$data %>%
  map(to_positive_class_percentage) %>%
  unlist()
configs$negative_pctg <- configs$data %>%
  map(to_negative_class_percentage) %>%
  unlist()
configs$data <- NULL
configs %>% arrange(mode)
```

Now we describe the exact data subsets related to each model.

## Presence of CIS-R Labels

This model will allow us to understand the profile of people with present suicide ideation.

- **Scopes**: wave 1 instances
- **General**: all instances
- **Restricted**: all instances with predictor `mentalvar_A_TMC`
- **Predictors**: baseline features
- **Outcomes**: *positive* wave 1 CIS-R labels

## Incidence of CIS-R Labels

This model will allow us to predict future appearance of suicide ideation.

- **Scopes**: wave 1 *negative* CIS-R labelled instances
- **General**: all instances
- **Restricted**: all instances with predictor `mentalvar_A_TMC`
- **Predictors**: baseline features
- **Outcomes**: *positive* wave 2 CIS-R labels

## Persistence of CIS-R Labels

This model will allow us to predict the continuation of suicide ideation.

- **Scope**: wave 1 *positive* CIS-R labelled instances
- **Predictors**: baseline features
- **Outcomes**: *positive* wave 2 CIS-R labels

## Remission of CIS-R Labels

This model will allow us to predict the future reduction/disappearance of suicide ideation.

- **Scope**: wave-1 *positive* CIS-R labelled instances
- **Predictors**: baseline features
- **Outcomes**: *negative* wave 2 CIS-R labels
